### 2017-07-29 README.Rmd
update md

```{r}
# simulate simple data structure
set.seed(1234)
n <- 500
W <- data.frame(W1 = runif(n,-2,2), W2 = rbinom(n,1,0.5))
A <- rbinom(n, 1, plogis(-2 + W$W1 - 2*W$W2))
Y <- rbinom(n, 1, plogis(-2 + W$W1 - 2*W$W2 + A))

@@

# get confidence intervals for means
ci_fit <- drconfint(fit)
# print the output
ci_fit

# get hypothesis test for means 
test_fit <- drtest(fit)
# print the output
test_fit
```
---

>>>>

```{r}
# load package
library(drtmle)

# simulate simple data structure
set.seed(1234)
n <- 200
W <- data.frame(W1 = runif(n,-2,2), W2 = rbinom(n,1,0.5))
A <- rbinom(n, 1, plogis(-2 + W$W1 - 2*W$W2))
Y <- rbinom(n, 1, plogis(-2 + W$W1 - 2*W$W2 + A))

@@

# get confidence intervals for means
ci_fit <- confint(fit)
# print the output
ci_fit

```
---
